Temporal ordering and registration of images in studies of developmental dynamics

### 2014-08-28 image_analysis_paper2/pnas_draft.tex
added stuff for paper

Because the developmental time of each embryo cannot be easily estimated, we have few options for validating our ordering. 
%
We compared the ordering obtained from vector diffusion maps to a manual ordering provided by a trained embryologist who is aware of the developmental progression and the important image features. 
%
The results, shown in  \fig~\ref{subfig:fixed_images_rank_corr}, show that our ordering is consistent with the manual ordering.
%
However, manually ordering the images is nontrivial for researchers who are not familiar with the developmental progression, and can be tedious and time-consuming for those who are.
%
In contrast, our method requires relatively little computational time, taking $15$~seconds on an Intel Core i7 2.93 GHz processor for $100$ images of $100 \times 100$ pixels, using 10$^{\circ}$ rotational discretizations.
%
Empirically, we found the computational time to be polynomial in the number of images, number of pixels, and the number of discretization points used to compute the pairwise rotations. 
%
The CPU time required was $\mathcal{O}(n)$ in the number of pixels and the number of rotations, and $\mathcal{O}(n^{1.5})$ in the number of images in the data set,.
%
Furthermore, the computation of the pairwise rotational alignments, which is the most computationally intensive portion of the calculation, is trivially parallelizable.
%
The requisite human intervention and tuning for our method is relatively small. 
%
Images must first be preprocessed so that the Euclidean distance between the pixels in informative; for our examples, this amounts to cropping the images to normalize the sizes of the embryo cross-sections, as well as blurring and normalizing the intensity of the nuclear signal, as the absolute intensity of this signal is not meaningful. 
%
%The image resolution should be chosen as low as possible while still retaining the important image features, as the computational cost increases with the number of pixels.
%
The two algorithmic parameters are the number of discretization points required to compute the pairwise alignments, and the kernel scale.
%
In our examples, we use 10$^{\circ}$ angle discretizations for the pairwise alignments, and one-tenth of the median pairwise distance for the kernel scale. 
%
We found that the results are not particularly sensitive to either of these parameters %(5$^{\circ}$--15$^{\circ}$ angle discretizations and kernel scales on the order of the median pairwise distances all yielded acceptable results)
, and that these parameter values were appropriate for all of the data sets presented in this paper. 
%
Image preprocessing and selecting these two parameters are relatively simple tasks compared to manual registration and ordering of images, especially when the data sets are large.  
%
Therefore, this methodology is very promising for much larger imaging data sets which are impractical to evaluate manually.

>>>>

Because the developmental time of each embryo cannot be easily estimated, we have few options for validating our ordering. 
%
We compared the ordering obtained from vector diffusion maps to a manual ordering provided by a trained embryologist who is aware of the developmental progression and the important image features. 
%
The results, shown in  \fig~\ref{subfig:fixed_images_rank_corr}, show that our ordering is consistent with the manual ordering.
%
However, manually ordering the images is nontrivial for researchers who are not familiar with the developmental progression, and can be tedious and time-consuming for those who are.
%
In contrast, our method requires relatively little computational time, taking $15$~seconds on an Intel Core i7 2.93 GHz processor for $100$ images of $100 \times 100$ pixels, using 10$^{\circ}$ rotational discretizations.
%
Empirically, we found the computational time to be polynomial in the number of images, number of pixels, and the number of discretization points used to compute the pairwise rotations. 
%
The CPU time required was $\mathcal{O}(n)$ in the number of pixels and the number of rotations, and $\mathcal{O}(n^{1.5})$ in the number of images in the data set,.
%
Furthermore, the computation of the pairwise rotational alignments, which is the most computationally intensive portion of the calculation, is trivially parallelizable.
%
The requisite human intervention and tuning for our method is relatively small. 
%
Images must first be preprocessed so that the Euclidean distance between the pixels in informative; for our examples, this amounts to cropping the images to normalize the sizes of the embryo cross-sections, as well as blurring and normalizing the intensity of the nuclear signal, as the absolute intensity of this signal is not meaningful. 
%
%The image resolution should be chosen as low as possible while still retaining the important image features, as the computational cost increases with the number of pixels.
%
The two algorithmic parameters are the number of discretization points required to compute the pairwise alignments, and the kernel scale.
%
In our examples, we use 10$^{\circ}$ angle discretizations for the pairwise alignments, and one-tenth of the median pairwise distance for the kernel scale. 
%
We found that the results are not particularly sensitive to either of these parameters (5$^{\circ}$--30$^{\circ}$ angle discretizations and kernel scales of one-fifth to one-twentieth of the median pairwise distances all yielded acceptable results)
, and that these parameter values were appropriate for all of the data sets presented in this paper. 
%
Image preprocessing and selecting these two parameters are relatively simple tasks compared to manual registration and ordering of images, especially when the data sets are large.  
%
Therefore, this methodology is very promising for much larger imaging data sets which are impractical to evaluate manually.
